Generating Correlated Data for Omics Simulation

### 2025-08-05 manuscript/paper.qmd
Clarify future directions section

While we describe one special form of $\Sigma_{\text{sim}}$ where generation is highly efficient, there exist many other possible covariance matrix forms.
Block diagonal covariance matrices are one such example which can efficiently represent even high-dimensional data [@Devijver02012018] and lend themselves to efficient simulation.
Sparse matrix methods [@Bien2011-nx; @Bickel_sparse; @Cai_adaptive] yield exactly zero correlation between some variables, but it is less clear how to simulate data from these efficiently.
Iterative sampling methods [@Krylov_subspaces] are one approach that could exploit the sparse nature and may even extend to sparse inverse covariance methods [@sparse_inverse_covariance].

>>>>

While we describe one special form of $\Sigma_{\text{sim}}$ where generation is highly efficient, there exist many other possible covariance matrix forms which are promising directions for future work.
Block diagonal covariance matrices are one such example which can efficiently represent even high-dimensional data [@Devijver02012018] and lend themselves to efficient simulation.
Other approaches include sparse matrix methods [@Bien2011-nx; @Bickel_sparse; @Cai_adaptive] which yield exactly zero correlation between some variables, but it is less clear how to simulate data from these efficiently.
Iterative sampling methods [@Krylov_subspaces] are one approach that could exploit the sparse nature and may even extend to sparse inverse covariance methods [@sparse_inverse_covariance].
